% Academic CV Template Based on leouieda/cv
% Adapted for Jilei Lin

\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\setmainfont{TeX Gyre Pagella}
\usepackage{hyperref, enumitem, titlesec}
\hypersetup{
  colorlinks=true,
  urlcolor=blue
}
\pagenumbering{gobble}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}
\titleformat{\subsection}{\bfseries\normalsize\raggedright}{}{0em}{}
\titlespacing*{\section}{0pt}{12pt plus 2pt}{6pt}
\titlespacing*{\subsection}{0pt}{10pt plus 2pt}{4pt}

\newcommand{\datedsubsection}[3]{
  \subsection*{#1 \hfill {\small #2 -- #3}}
}

\begin{document}

\begin{center}
  {\LARGE \textbf{Jilei Lin}} \\[4pt]
  Department of Biostatistics, George Washington University \\
  \href{mailto:jileilin@email.com}{jileilin@email.com} $\cdot$ Washington, DC\\
  \href{https://github.com/jileil2}{github.com/jileil2} $\cdot$ \href{https://www.linkedin.com/in/jileilin}{LinkedIn}
\end{center}

\section*{Research Interests}
Spatial quantile regression, large-scale data modeling, distributed inference, climate and health, biostatistical applications.

\section*{Education}
\datedsubsection{Ph.D. in Biostatistics}{George Washington University}{Expected 2025}
\begin{itemize}[leftmargin=*]
  \item Dissertation: Scalable Spatial Quantile Regression and Applications in Climate and Health
  \item Advisor: Prof. Lily Wang
\end{itemize}

\datedsubsection{M.S. in Biostatistics}{George Washington University}{2021}
\datedsubsection{B.S. in Mathematics}{University Name}{2018}

\section*{Research Experience}
\datedsubsection{Graduate Research Assistant}{GWU}{2021--Present}
\begin{itemize}[leftmargin=*]
  \item Developed methods in censored bent line quantile regression.
  \item Collaborated on EAMG data analysis with Dr. Jie Luo.
  \item Applied distributed inference for large spatial quantile models.
\end{itemize}

\datedsubsection{Research Assistant, Speech and Hearing Science}{GWU}{2022--2024}
\begin{itemize}[leftmargin=*]
  \item Applied linear mixed models to analyze behavioral datasets.
  \item Assisted Dr. Mackenzie Fama in grant proposal writing and statistical consultation.
\end{itemize}

\section*{Publications}
\begin{itemize}[leftmargin=*]
  \item Lin, J. \& Wang, L. (2024). "Distributed Spatial Quantile Regression with Convolution-Smoothed Loss." Under Review.
  \item Lin, J. et al. (2023). "Censored Quantile Models for Autoimmune Disorders." Submitted.
\end{itemize}

\section*{Software}
\begin{itemize}[leftmargin=*]
  \item \texttt{SQBiT} (Spatial Quantile Bootstrap Inference Tool): R package for spatial quantile analysis \href{https://github.com/jileil2/SQBiT}{[GitHub]}
  \item Contributor to \texttt{BPST} and \texttt{Triangulation} R packages
\end{itemize}

\section*{Teaching Experience}
\datedsubsection{Graduate Teaching Assistant}{GWU Biostatistics Department}{2021--2023}
\begin{itemize}[leftmargin=*]
  \item TA for courses in regression, statistical inference, and computing in R.
\end{itemize}

\section*{Skills}
R, Python, LaTeX, Git, ADMM, Adam optimizer, spatial modeling, quantile regression

\section*{References}
Available upon request.

\end{document}